Social Conditions of Fear

### 2023-12-04 scripts/manuscript.qmd
figure out how to do word count in Quarto
methods

@@

>>>>

I'm leaving myself a note here to figure out how to do word count in a Quarto document. This will allow me to directly write in the qmd file and save the trouble of writing elsewhere like a word document and pasting things here.

@@

This study draws data from the General Social Survey (GSS). The GSS is a nationally representative interview-based survey that has collected longitudinal data since 1972. The GSS contains questions on demographics, behaviors, attitudes, civil liberaties, crime and violence, intergroup tolerance, morality, national spending priorities, psychological well-being, social mobility, stress, and traumatic events. Our study is limited to data collected during the 2022 wave and we draw primarily on demographic and well-being variables.
